%
\begin{frame}[t]%
\expandafter\frametitle{\sharedSlideTitle}%
%
\locateGraphic{1}{width=0.85\paperwidth}{\sharedDir/graphics/optimization_superlatives/optimization_superlatives}{0.075}{0.18}%
\locate{1}{\parbox{0.33\paperwidth}{\noindent\footnotesize%
The \emph{superlative} form of an adjective is used to show that something has a quality to the greatest or least degree.%
}}{0.65}{0.86}%
%
\locateGraphic{2}{width=0.35\paperwidth}{\sharedDir/graphics/optimization_superlatives/optimization_superlatives_shortest}{0.63}{0.01}%
\locateGraphic{3}{width=0.35\paperwidth}{\sharedDir/graphics/optimization_superlatives/optimization_superlatives_least}{0.63}{0.01}%
\locateGraphic{4}{width=0.35\paperwidth}{\sharedDir/graphics/optimization_superlatives/optimization_superlatives_fewest}{0.63}{0.01}%
\locateGraphic{5}{width=0.35\paperwidth}{\sharedDir/graphics/optimization_superlatives/optimization_superlatives_earliest}{0.63}{0.01}%
\locateGraphic{6}{width=0.35\paperwidth}{\sharedDir/graphics/optimization_superlatives/optimization_superlatives_longest}{0.63}{0.01}%
\locateGraphic{7}{width=0.35\paperwidth}{\sharedDir/graphics/optimization_superlatives/optimization_superlatives}{0.63}{0.01}%
%
\locateGraphic{2}{width=0.4\paperwidth}{\sharedDir/graphics/hfuu_campus_map/hfuu_campus_map}{0.1}{0.27}%
\locateGraphic{2}{width=0.4\paperwidth}{\sharedDir/graphics/hfuu_campus_map/hfuu_campus_map_01_start_goal}{0.1}{0.27}%
%
\locateGraphic{3}{width=0.5\paperwidth}{\sharedDir/graphics/transport/transport}{0.35}{0.33}%
%
\locateGraphic{4}{width=0.8\paperwidth}{\sharedDir/graphics/bin_packing/bin_packing}{0.1}{0.47}%
%
\locateGraphic{5}{width=0.42\paperwidth}{\sharedDir/graphics/jssp_production_diagram/jssp_production_diagram}{0.29}{0.516}%
%
\locateGraphic{6}{width=0.5\paperwidth}{\sharedDir/graphics/wireless_network/wireless_network}{0.62}{0.32}%
%
\locate{}{\parbox{0.95\paperwidth}{\noindent%
\begin{itemize}%
\item Optimization means finding superlatives.%
%
\item<2-> Find the \alert{shortest} path from start to goal.%
%
\item<3-> Pick up and deliver packages from different places\\to customers using the \alert{least} amount of fuel.%
%
\item<4-> Pack a set of things into the \alert{fewest} boxes.%
%
\item<5-> Assign tasks to machines such that we can finish our work the at \alert{earliest}\only<-5>{ }\only<6->{\\}possible time.%
%
\item<6-> Find a strategy to manage the power of the nodes in this sensor\\network so that full coverage is guaranteed for the \alert{longest}\\possible duration.%
%
\item<7-> And so on.%
\end{itemize}%
}}{0.025}{0.0875}%
%
\end{frame}%
%
